Piecewise Regression for Nutritional Outcomes Pre- and Post-CFTR Modulator

### 2022-05-18 StatNet/knot_models.qmd
Update knot_models.qmd

@@

    -   Most patients have multiple nutrition measures before and after CFTR modulator start.
    -   A subset of patients were on ivacaftor followed by elexacaftor/tezacaftor/ivacaftor (ETI).

@@

>>>>

## Introduction

-   Exocrine pancreatic insufficiency (PI) is present from birth in up to two thirds of patients with CF
-   85% of patients with CF ultimately have PI with associated fat malabsorption by one year of age
-   Malabsorption puts persons with CF at risk for fat-soluble vitamin deficiencies.

## Introduction

-   People with CF rely on supplemental pancreatic enzyme replacement therapy (PERT) in addition to a diet high in protein, calories, fat-soluble vitamins, and salt.
-   Highly effective CFTR modulators, ivacaftor and elexacaftor/tezacaftor/ivacaftor (ETI), substantially improve CFTR activity, lung function and nutritional status.
-   Their impact on other markers of nutrition, particularly fat-soluble vitamin absorption, are still unclear.

@@

    -   Most patients have multiple nutrition measures before and after CFTR modulator start.
    -   A subset of patients were on ivacaftor followed by ETI.

@@

-   Retrospective study of children with CF included individuals ages 4-21 followed at Children's Hospital Colorado (CHCO) from January 1982 to July 2021.

-   Criteria were a diagnosis of CF based on sweat chloride $\geq$ 60mmol/L or two CFTR gene mutations.

## First Analysis
